---
title: "Assignment1"
author: "YANG Mengwei"
date: "9/30/2017"
output: html_document
---

##Exercice1
I wanted to creat a SSH key, and I did creat one but I don't know how to use it,always error messages.....

##Exercice2
```{r}
possible_outcomes <- c(0, 1, 2, 3, 4, 5)
outcome_probabilities <- c(0.1, 0.5, 0.2, 0.1, 0.05, 0.05)
n_data_points <- 400

set.seed(1)
fake_data_points <- sample(possible_outcomes,
                           n_data_points,
                           replace=T,
                           prob=outcome_probabilities)
set.seed(NULL)

fake_data_set <- tibble::data_frame(`Fake measurement`=fake_data_points)
```
My guess for Chunk1 of R is that : this chunk genere a set of numbers combined by 0,1,2,3,4,5, the probabilities of these numbers in this set are the values in vector outcome_probabilities and respectively ---->0(0.1),1(0.5),2(0.2),3(0.1),4(0.05),5(o.o5), and the number of items of this set is absolutely under 400, which is the value of n_data_points. This set of numbers is randomly generated with different number of itmes, colonnes and lines, but the total number of items is always less than 400. I have this guess because:

* first, according to the video I know '<-' is to defin a variable, so I know possible_outcomes, outcome_probabilities and fake_data_points are vectors who have a set of variables, and n_data_points is a variable just have one value. For these variables, their names give me the impression what they are.

* seconde, I run this chunk and generate a set of numbers composed by items of possible_outcomes, and this set has 40 items every line and the last line stared with 361, that reminds me the number of n_data_points, so I guess this variale defin the biggest number of items in this set.

* third, in the beginning this chunk counld't be run because lack of the package "tibble", and I search the information of this package in Internet, then I know this packge is to create data frames, and the parametres of this function are defined in fake_data_points.

* fourth, the fake_data_points is generated by a function named "sample", and I learn in Internet that "sample"" function is for taking a sample of the specified size from a bunch of variables(a vector). The grammair is sample(the variables we take, the size, replace = FALSE, prob = NULL/we can define)

* fifth, what I'm not very clear is the function "set.seed". When I delete the set.seed(1), in the result there are totally 400 lines and one variable every line, from this I can understand what the Internet say "useful to creating random objects that can be reproduced." But I'm  a little confused by other explications.

```{r}
ggplot2::ggplot(fake_data_set, ggplot2::aes(x=`Fake measurement`)) +
  ggplot2::geom_histogram(bins=5, colour="black", fill="lightgrey")
```

##Exercice3

##Exercice4

##Exercice5

##Exercice6